Network Structure, Efficiency, and Performance in WikiProjects

### 2017-08-02 paper.tex
More outline and citations.

\section{Introduction}
\epigraph
{The problem with Wikipedia is that it only works in practice. In theory, it can never work.}
{Miikka Ryokas\cite{latest_cohen_2007}}

@@

\section{Methods}

@@

For performance, we wish to quantify how good articles tend to be when they reach a stable state.
Measuring performance is difficult for several reasons:
there is no objective meaasure of article quality avaialbe,
and articles are always changing, making it difficult to know which articles should be considered
complete or stable.
We use an extremely simple performance measure that gives surprisingly consistent results.
In addition to per-project quality assessment, articles can be given ``featured article'' or
``good article'' status.
The criteria for these statuses are consistent across all of Wikipedia,
and any editor can participate in the discussion and decision to award good or featured
status.
In other words, the good and featured statuses are more objective than per-project assessments.
Our performance measure $P(W)$ is just the percentage of articles in project $W$ which have reached
good or featured status:
\beq
P(W) &=& \frac{f(W) + g(W)}{n(W)},
\eeq
where $f(W)$ and $g(W)$ are the numbered of featured and good articles respectively,
and $n(W)$ is the total number of articles
\subsection{Coeditor Networks}

@@

\subsection{Numerical Simulation}

@@

\section{Results}
TODO

>>>>

\section{Introduction}
\epigraph
{The problem with Wikipedia is that it only works in practice. In theory, it can never work.}
{Miikka Ryokas \cite{cohen_latest_2007}}

@@

\section{Empirical Methods}

@@

For performance, we wish to quantify how good articles tend to be when they reach a stable state.
Measuring performance is difficult for several reasons:
there is no objective meaasure of article quality avaialbe,
and articles are always changing, making it difficult to know which articles should be considered
complete or stable.
We use an extremely simple performance measure that gives surprisingly consistent results.
In addition to per-project quality assessment, articles can be given ``featured article'' or
``good article'' status.
The criteria for these statuses are consistent across all of Wikipedia,
and any editor can participate in the discussion and decision to award good or featured
status.
In other words, the good and featured statuses are more objective than per-project assessments.
Our performance measure $P(W)$ is just the percentage of articles in project $W$ which have reached
good or featured status:
\beq
P(W) &=& \frac{f(W) + g(W)}{n(W)},
\eeq
where $f(W)$ and $g(W)$ are the numbered of featured and good articles respectively,
and $n(W)$ is the total number of articles.

\subsection{Coeditor Networks}

@@

\subsection{Empirical Results}

@@

\section{Numerical Simulation}

Intro

\subsection{Learning Strategies}

Individual learning

Social learning and iteration

Best neighbor

Conformity

Consensus

\subsection{Network family}

Base network

Duplication and rewiring

\subsection{Simulation results}
